### 2018-07-08 latex/discussion.tex
Minor formatting changes before sending manuscript for internal review

--> Why was the yeast MT defined as NNMT?

--> Are there any ideas where the NNMT came from?

--> Any information on the methylation activity (also in comparison to others)? Does it fit to the found kinetic functions?

@@

--> NADS needed for \textit{de~novo} pathway

--> NMNAT also needed in NamPRT and \textit{de~novo} pathway

-----> Is the \textit{de~novo} pathway still necessary? If we take up enough Vit B3 with the diet, why \textit{de~novo}?

--> NAPRT needed for NA that is taken up with the diet (and if NA is processed, the other two enzymes are also needed to continue processing)

+

>>>>

-- Why was the yeast MT defined as NNMT?

-- Are there any ideas where the NNMT came from?

-- Any information on the methylation activity (also in comparison to others)? Does it fit to the found kinetic functions?

@@

-- NADS needed for \textit{de~novo} pathway

-- NMNAT also needed in NamPRT and \textit{de~novo} pathway

---- Is the \textit{de~novo} pathway still necessary? If we take up enough Vit B3 with the diet, why \textit{de~novo}?

-- NAPRT needed for NA that is taken up with the diet (and if NA is processed, the other two enzymes are also needed to continue processing)

### 2018-07-08 latex/introduction.tex
Minor formatting changes before sending manuscript for internal review

Due to the constant release of Nam through NAD-consuming signalling reactions, the NAD salvage pathway using Nam as precursor is the most important NAD synthesis pathway. If Nam would not be constantly recycled into NAD, humans would require a much higher daily vitamin B3 intake than the 16\,mg that are the current daily recommendation \cite{CommissionofEuropeanCommunities2008}. In the first step of the salvage pathway, Nam is converted to the mononucleotide NMN by the Nam phosphoribosyltransferase (NamPRT) using phosphoribosyl pyrophosphate (PRPP) as co-substrate. The nearly complete recycling of Nam is achieved by an extraordinary high affinity of NamPRT to Nam, the $K_{M}$ being in the low nanomolar range \cite{Burgos2008}. This extraordinary affinity appears to be mediated by an ATP-dependent phosphorylation of a histidine residue in the catalytic core \todo{Needs reference}. Despite the importance of its salvage, Nam can also be marked for excretion by methylation. The presence of nicotinamide N-methyltransferase (NNMT) in vertebrates \cite{Gossmann2012FEBS} is among the most enigmatic and counterintuitive features of NAD metabolism. While NamPRT is seemingly optimised to recycle even the faintest amounts of Nam back into NAD synthesis, NNMT seems to have no metabolic function other than to remove Nam from NAD metabolism. This puzzle becomes even more intriguing when considering that the majority of lower organisms and plants deamidate Nam to nicotinic acid (NA) using the nicotinamide deamidase (NADA) before it can enter NAD biosynthesis via the Preiss-Handler pathway (fig.~\ref{fig:pathway_overview}).

>>>>

Due to the constant release of Nam through NAD-consuming signalling reactions, the NAD salvage pathway using Nam as precursor is the most important NAD synthesis pathway. If Nam would not be constantly recycled into NAD, humans would require a much higher daily vitamin B3 intake than the 16\,mg that are the current daily recommendation \cite{CommissionofEuropeanCommunities2008}. In the first step of the salvage pathway, Nam is converted to the mononucleotide NMN by the Nam phosphoribosyltransferase (NamPRT) using phosphoribosyl pyrophosphate (PRPP) as co-substrate. The nearly complete recycling of Nam is achieved by an extraordinary high affinity of NamPRT to Nam, the $K_{M}$ being in the low nanomolar range \cite{Burgos2008}. This extraordinary affinity appears to be mediated by an ATP-dependent phosphorylation of a histidine residue in the catalytic core\todo{Needs a reference}. Despite the importance of its salvage, Nam can also be marked for excretion by methylation. The presence of nicotinamide N-methyltransferase (NNMT) in vertebrates \cite{Gossmann2012FEBS} is among the most enigmatic and counterintuitive features of NAD metabolism. While NamPRT is seemingly optimised to recycle even the faintest amounts of Nam back into NAD synthesis, NNMT seems to have no metabolic function other than to remove Nam from NAD metabolism. This puzzle becomes even more intriguing when considering that the majority of lower organisms and plants deamidate Nam to nicotinic acid (NA) using the nicotinamide deamidase (NADA) before it can enter NAD biosynthesis via the Preiss-Handler pathway (fig.~\ref{fig:pathway_overview}).
